\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-16 docs/paper/paper.tex
updata: comp-performance

\begin{table}[h]
\begin{tabular}{lllll}
    & data set size & mini batch size & Time elapsed (sec) \\
Mini batches    &336 + 0 & 8 & 136 & \\
    &336 + 1000 & 8 & 388 & \\
    &336 + 2000 & 16 & 563  & \\ 
    &336 + 3000 & 20 & 958  & \\
\end{tabular}
\begin{tabular}{lllll}
   & data set size & Time elapsed (sec) \\
Full batch    &336 + 0 &  96 & \\
    &336 + 1000 &  162 & \\
    &336 + 2000 &  165 & \\ 
    &336 + 3000 &  263 & \\
\end{tabular}
\caption{Training performance using Tensorflow/Keras}
\end{table}
\begin{table}[h]
\begin{tabular}{lllll}
 & data set size & mini batch size & Time elapsed (sec) \\
Mini batches    & 336 + 0 & 8 & 359 & \\
    & 336 + 1000 & 8 & 1348  & \\
    & 336 + 2000 & 16 & 1379  & \\ 
    & 336 + 3000 & 20 & 1504 & \\
\end{tabular}
\begin{tabular}{lllll}
   &data set size & Time (sec) \\
   Full batch &336 + 0 &  14  & \\
    & 336 + 1000 &  57  & \\
    & 336 + 2000 &  107  & \\ 
    & 336 + 3000 &  195  & \\
\end{tabular}
\caption{Training performance using Pytorch}
\end{table}

>>>>

\begin{table}[h]
\begin{tabular}{lllll}
    & data set size & mini batch size & Time elapsed (sec) \\
Mini batches    &336 + 0 & 8 & 214 & \\
    &336 + 1000 & 8 & 744 & \\
    &336 + 2000 & 16 & 685  & \\ 
    &336 + 3000 & 20 & 861  & \\
\end{tabular}
\begin{tabular}{lllll}
   & data set size & Time elapsed (sec) \\
Full batch    &336 + 0 &  23 & \\
    &336 + 1000 &  34 & \\
    &336 + 2000 &  45 & \\ 
    &336 + 3000 &  57 & \\
\end{tabular}
\caption{Training performance using Tensorflow(Keras)}
\end{table}
\begin{table}[h]
\begin{tabular}{lllll}
 & data set size & mini batch size & Time elapsed (sec) \\
Mini batches    & 336 + 0 & 8 & 1315 & \\
    & 336 + 1000 & 8 & 6453  & \\
    & 336 + 2000 & 16 & 4751  & \\ 
    & 336 + 3000 & 20 & 5132 & \\
\end{tabular}
\begin{tabular}{lllll}
   &data set size & Time (sec) \\
   Full batch &336 + 0 &  36  & \\
    & 336 + 1000 &  98  & \\
    & 336 + 2000 &  195  & \\ 
    & 336 + 3000 &  336  & \\
\end{tabular}
\caption{Training performance using Pytorch}
\end{table}
